Scheeper's Meager-NWD Game and the Menger Game

### 2015-02-20 phd/dissertation/chapter1.tex
revisions suggested by outside reader

A winning $k+1$-Markov strategy for $\gruConGame{X}{x}$ may be improved to
a winning Markov strategy; however, it remains open whether this same
result holds true for $\gruKPGame{X}$. The chapter on $\gruKPGame{X}$ concludes
with a class of spaces which may seem to provide a counterexample at first,
however:

>>>>

A winning $(k+1)$-Markov strategy for $\gruConGame{X}{x}$ may be improved to
a winning Markov strategy; however, it remains open whether this same
result holds true for $\gruKPGame{X}$. The chapter on $\gruKPGame{X}$ concludes
with a class of spaces which may seem to provide a counterexample at first,
however:

### 2015-02-20 phd/dissertation/chapter2.tex
revisions suggested by outside reader

This chapter outlines the set-theoretic and game-theoretic preliminaries
required for this paper.

@@

This concept of when (and how) a player can ``force'' a win in certain
topological games is the focus of this manuscript.

>>>>

This chapter outlines the set-theoretic and game-theoretic preliminaries
required for this dissertation.

@@

This concept of when (and how) a player can ``force'' a win in certain
topological games is the focus of this dissertation.

### 2015-02-20 phd/dissertation/chapter3.tex
revisions suggested by outside reader

We begin by investigating a game due to Gary Gruenhage, introduced in
his doctoral dissertation to solve a problem due to Phil Zenor.

@@

Due to the equivalency of the ``hard'' and ``normal'' variations of the
convergence game in the perfect information case, many authors use them
interchangibly. However, it is possible to find spaces for which the games are
not equivalent when considering $k+1$-tactics and $k+1$-marks, as we will
soon see.

@@

As an example, the existence of a winning coding strategy is necessary for the
second player to force a win the Banach-Mazur game.

>>>>

We begin by investigating a game due to Gary Gruenhage, introduced in
his doctoral dissertation to solve a problem due to Phil Zenor
\cite{MR0394561}.

@@

Due to the equivalency of the ``hard'' and ``normal'' variations of the
convergence game in the perfect information case, many authors use them
interchangibly. However, it is possible to find spaces for which the games are
not equivalent when considering $(k+1)$-tactics and $(k+1)$-marks, as we will
soon see.

@@

As an example, the existence of a winning coding strategy is necessary for the
second player to force a win in the Banach-Mazur game.

### 2015-02-20 phd/dissertation/chapter5.tex
revisions suggested by outside reader

\begin{proof}
  Let $\sigma$ be a winning $k+1$-mark for $\pl K$ such that $m\leq n$ and
  $\ran r \subseteq \ran s$ implies $\sigma(r,m)\subseteq\sigma(s,n)$.
  For a sequence $p$, let $p\rest^k n=\nu_k(p\rest n)$ give the last $k$
  terms of $p\rest n$.

  Define $r:\pmb X\to\omega$ by
    \[
      r(\pmb x)
        =
      \left\{
        \begin{array}{lcl}
          |s|
        & : &
          \pmb x = \<x,s\> \in X\times 2^{<\omega}
        \\
          0
        & : &
          \pmb x \in C
        \end{array}
      \right.
    \]
  and use $r$ to define the $k+1$-tactic $\tau$ by
    \[
      \tau(\emptyset)
        =
      \sigma(\emptyset,0)
    \]
    \[
      \tau(\pmb t\concat\<\pmb x\>)
        =
      L_{r(\pmb x)+1}
        \cup
      \{\pmb x\}
        \cup
      \sigma(\pmb t\concat\<\pmb x\>,r(\pmb x)+1)
    \]

@@

  Denoting $\pmb q(n)=\<x_n,s_n\>$, it's trivial to note that $|s_0|\geq 0$.
  Assuming that $|s_m|\geq m$ for $m\leq n$,
  it then follows that
    \[
      \pmb q(n+1)
        =
      \pmb p(f(n+1))
        \not\in
      \bigcup_{m\leq f(n+1)}\tau(\pmb p\rest^{k+1} m)
    \]
    \[
        \supseteq
      \bigcup_{m\leq n}\tau(\pmb q\rest^{k+1} m)
        \supseteq
      \sigma(\emptyset,0)
        \cup
      \bigcup_{m < n}\sigma(\pmb q\rest^{k+1} (m+1),|s_m|+1)
    \]
    \[
        \supseteq
      \sigma(\emptyset,0)
        \cup
      \bigcup_{m < n}\sigma(\pmb q\rest^{k+1} (m+1),m+1)
    \]
  and
    \[
      \pmb q(n+1)
        \not\in
      \tau(\pmb q\rest^{k+1} (n+1))
        \supseteq
      L_{r(\pmb q(n))}
        =
      L_{|s_n|+1}
    \]
  gives $|s_{n+1}|\geq|s_n|+1\geq n+1$.
  Thus $\pmb q$ is a legal attack on the winning $k+1$-Markov strategy
  $\sigma$, so the collection $\{\{\pmb q(n)\}:n<\omega\}$ is locally finite.
  and it follows that $\{\{\pmb p(n)\}:n<\omega\}$ is also locally finite.
\end{proof}

@@

\begin{proof}
  Let $Y$ be a zero-dimensional Corson compact space which is not Eberlein
  compact; one such space was constructed in \cite{Marciszewski1991291}.
  >et $X=Y^2$.
  Then by characterizations of Corson and Eberlien compacts found in
  \cite{MR752278},
  $Y^2\setminus\Delta$ is meta-Lindel\"of but not $\sigma$-metacompact, so
  there exists a point-countable clopen cover $\mc U$ of $Y^2\setminus\Delta$
  which is not $\sigma$-point-finite. Then $\mc U\cup\{X\}$ is a point-countable
  clopen cover of $X$ which is not $\sigma$-point-finite.
\end{proof}

>>>>

\begin{proof}
  Let $\sigma$ be a winning $(k+1)$-mark for $\pl K$ such that $m\leq n$ and
  $\ran r \subseteq \ran s$ implies $\sigma(r,m)\subseteq\sigma(s,n)$.
  For a sequence $p$, let $p\rest^k n=\nu_k(p\rest n)$ give the last $k$
  terms of $p\rest n$.

  Define $r:\pmb X\to\omega$ by
    \[
      r(\pmb x)
        =
      \left\{
        \begin{array}{lcl}
          |s|
        & : &
          \pmb x = \<x,s\> \in X\times 2^{<\omega}
        \\
          0
        & : &
          \pmb x \in C
        \end{array}
      \right.
    \]
  and use $r$ to define the $(k+1)$-tactic $\tau$ by
    \[
      \tau(\emptyset)
        =
      \sigma(\emptyset,0)
    \]
    \[
      \tau(\pmb t\concat\<\pmb x\>)
        =
      L_{r(\pmb x)+1}
        \cup
      \{\pmb x\}
        \cup
      \sigma(\pmb t\concat\<\pmb x\>,r(\pmb x)+1)
    \]

@@

  Denoting $\pmb q(n)=\<x_n,s_n\>$, it's trivial to note that $|s_0|\geq 0$.
  Assuming that $|s_m|\geq m$ for $m\leq n$,
  it then follows that
    \[
      \pmb q(n+1)
        =
      \pmb p(f(n+1))
        \not\in
      \bigcup_{m\leq f(n+1)}\tau(\pmb p\rest^{k+1} m)
    \]
    \[
        \supseteq
      \bigcup_{m\leq n}\tau(\pmb q\rest^{k+1} m)
        \supseteq
      \sigma(\emptyset,0)
        \cup
      \bigcup_{m < n}\sigma(\pmb q\rest^{k+1} (m+1),|s_m|+1)
    \]
    \[
        \supseteq
      \sigma(\emptyset,0)
        \cup
      \bigcup_{m < n}\sigma(\pmb q\rest^{k+1} (m+1),m+1)
    \]
  and
    \[
      \pmb q(n+1)
        \not\in
      \tau(\pmb q\rest^{k+1} (n+1))
        \supseteq
      L_{r(\pmb q(n))}
        =
      L_{|s_n|+1}
    \]
  gives $|s_{n+1}|\geq|s_n|+1\geq n+1$.
  Thus $\pmb q$ is a legal attack on the winning $(k+1)$-Markov strategy
  $\sigma$, so the collection $\{\{\pmb q(n)\}:n<\omega\}$ is locally finite.
  and it follows that $\{\{\pmb p(n)\}:n<\omega\}$ is also locally finite.
\end{proof}

@@

\begin{proof}
  Let $Y$ be a zero-dimensional Corson compact space which is not Eberlein
  compact; one such space was constructed in \cite{Marciszewski1991291}.
  Let $X=Y^2$.
  Then by characterizations of Corson and Eberlien compacts found in
  \cite{MR752278},
  $Y^2\setminus\Delta$ is meta-Lindel\"of but not $\sigma$-metacompact, so
  there exists a point-countable clopen cover $\mc U$ of $Y^2\setminus\Delta$
  which is not $\sigma$-point-finite. Then $\mc U\cup\{X\}$ is a point-countable
  clopen cover of $X$ which is not $\sigma$-point-finite.
\end{proof}
